GPU-friendly Stroke Expansion

### 2024-04-24 paper.tex

% TODO: caps/joins figure highlighting mapping of segments, joins, and caps to threads, encoding. Make sure to show the straight-line inner join.
% TODO: visualize per-segment flattened output for a fill and for a stroke from the perspective of one thread.
% TODO: finish this \begin{algorithm} snippet
\begin{algorithm}
  $tid \gets$ global invocation ID\;
  $(style, segment) \gets readScene(tid)$\;
  \eIf{$style$ is $fill$}{
      output source curve\;
  }{
      \tcp{Handle stroked segment}
      \eIf{$segment$ is \emph{stroke cap marker}}{
          \eIf{path is open}{output start cap\;}{output nothing\;}
      }{
          output both offset curves\;
          $neighbor \gets readScene(tid + 1)$\;
          \eIf{$neighbor$ is not \emph{stroke cap marker} OR path is closed}{
              output join\;
          }{
              output end cap\;
          }
      }
  }
\caption{The control flow of the compute shader}
\label{alg:shader-flow}
\end{algorithm}

Each thread outputs a polyline that fits a subset of the rendered subpath's outer contour, represented by the path segment. For a filled primitive, a thread only outputs the flattened approximation of the path segment. For a stroke, a thread outputs the polylines approximating multiple curves: a) the two parallel curves on both sides of the source segment, offset by the desired stroke \emph{halfwidth}, and b) the joins that connect the path segment to the next adjacent segment. We also store metadata in our input encoding that marks the position of a path segment within the containing subpath. We use this information to determine whether to output an end cap instead of a join. We encode one additional segment designated as the \emph{stroke cap marker} for every subpath. The thread assigned to the marker segment only outputs a start cap, which completes the stroke outline.

@@

% TODO: explain flatten_euler

>>>>

\begin{center}
\begin{figure}
    \includegraphics[scale=0.18]{stroke_threads}
    \caption{Visualization of contour outlines and the IDs of GPU threads that flatten them. The subpath contains two adjacent cubic Bézier curves rendered as both a stroke and a fill. In the stroked version, thread $n$ flattens the offset curves of the first curve (blue) and the join segment with the miter style (dark blue). Thread $n + 1$ flattens the offset curves of the second curve (orange) and the end cap with the round style (dark orange). Thread $n + 2$ is assigned the \emph{subpath end segment} and flattens the start cap (red). When the same path is rendered as a fill, threads $n$ and $n + 1$ each flatten the source curves, while thread $n + 2$ outputs the \emph{close} segment that joins the end of the subpath to its starting point. The black arrows represent the winding direction of the output segments.}
    \Description{TODO}
    \label{fig:stroke_threads}
\end{figure}
\end{center}

\begin{algorithm}
  $tid \gets$ global invocation ID\;
  $(style, segment) \gets readScene(tid)$\;
  \eIf{$style$ is $fill$}{
      output source curve\;
  }{
      \tcp{Handle stroked segment}
      \eIf{$segment$ is \emph{stroke cap marker}}{
          \eIf{path is open}{output start cap\;}{output nothing\;}
      }{
          output both offset curves\;
          $neighbor \gets readScene(tid + 1)$\;
          \eIf{$neighbor$ is not \emph{stroke cap marker} OR path is closed}{
              output join\;
          }{
              output end cap\;
          }
      }
  }
\caption{The control flow of the compute shader}
\label{alg:shader-flow}
\end{algorithm}

Each thread outputs a polyline that fits a subset of the rendered subpath's outer contour, represented by the path segment (see Figure \ref{fig:stroke_threads}). For a filled primitive, a thread only outputs the flattened approximation of the path segment. For a stroke, a thread outputs the polylines approximating multiple curves: a) the two parallel curves on both sides of the source segment, offset by the desired stroke \emph{halfwidth}, and b) the joins that connect the path segment to the next adjacent segment. We also store metadata in our input encoding that marks the position of a path segment within the containing subpath. We use this information to determine whether to output an end cap instead of a join. We encode one additional segment designated as the \emph{stroke cap marker} for every subpath. The thread assigned to the marker segment only outputs a start cap, which completes the stroke outline.

@@

% TODO: explain flatten_euler
% TODO: visualize per-segment flattened output for a fill and for a stroke from the perspective of one thread.
